Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2016-05-20 paper1.tex
last of casey changes

\begin{abstract}
\noindent
The distribution of massive clusters of galaxies depends strongly on the total cosmic mass density, the mass variance, and the dark energy equation of state. As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observations of clusters can lead to accurate estimates of their total masses. Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion using probability based and machine learning methods. We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will employ new Visible Integral-Field Replicable Unit Spectrographs (VIRUS), over 420 \degsq\ on the sky with a 1/4.5 fill factor. VIRUS covers the blue/optical portion of the spectrum ($3500-5500~\AAA$), allowing surveys to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$). We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field. For both surveys, we include realistic uncertainties from galaxy magnitude and line-flux limits. We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities. With HETDEX, we can recover cluster masses to $\sim0.1$ dex which can be further improved to $<0.1$ dex with targeted follow-up observations. This level of cluster mass recovery enables constraints on $\sigma_8$ to $<20$\%, and the unique properties of the observations will provide important calibrations for the optical richness-cluster mass relation.
\end{abstract}
% Using both observing strategies, we produce cluster mass probability density functions $P(M_{200c}|\vec{x})$ of a cluster mass ($M_{200c}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$.
% \end{abstract}

@@

The second broad method is the direct calibration of cluster masses. This recipe has two distinct but not always independent tracks. The ``direct'' method uses observations of a relatively small set of clusters and then uses known mass estimators, including X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, microwave observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass. This directly calibrates the observable-mass relation which is then applied to a much larger sample. The complications lie in that the ``true'' masses are, in fact, estimations, and the methods used to recover these cluster masses are subject to their own limitations. X-ray based cluster masses assume hydrostatic equilibrium \citeeg{Mantz2015} which may only be valid for a very small number and range of cluster masses. The Sunyaev-Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up-scattering of cosmic microwave background (CMB) photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}. WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters (where the lensing signal is particularly weak), and potentially suffer from line-of-sight effects as WL is sensitive to all mass along the line-of-sight. Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffer from systematics due to cluster formation physics which disrupts the velocity field.

@@

Large-area sky surveys, both on going and planned, are revolutionizing cluster cosmology using a large range of wavelengths. The South Pole Telescope (SPT; \citealt{Carlstrom2011}) and the Atacama Cosmology Telescope (ACT; \citealt{Swetz2011}) are discovering many clusters through the SZE. Optically, the on going Dark Energy Survey (DES; \citealt{DES2005}) and planned Large Synoptic Survey Telescope (LSST; \citealt{LSST2012}) will identify many thousands of clusters to much lower masses than is possible with SZE measurements. However, regardless of the discovery method used, spectroscopic follow-up is needed to further constrain $P(M|z,X)$. But as the cluster dataset grows to many tens of thousands of clusters individual follow-up becomes increasingly impractical. Therefore, large spectroscopic surveys are needed to more fully constrain the observable--mass relation of clusters.

@@

@@

\subsection{Conditional [\ion{O}{ii}] Flux Probability Distribution Functions}\label{sec: oii luminosity}
\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
	\caption{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points. The two colored boxes show regions containing potential catalog galaxies. \textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right. The [\ion{O}{ii}] luminosities are assigned to catalog galaxies from slice sampling the probability histogram and converted to fluxes using the redshift of each galaxy.} \label{fig: oii sdss} 
\end{figure*}
We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{ii}] emission line strengths to the galaxies in the Buzzard catalog. We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{ii}] line flux signal-to-noise of five. Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies.

@@

Figure~\ref{fig: oii sdss} illustrates this process. The numbered boxes in the left panel show the bins corresponding to two example Buzzard galaxies ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$). The right panel shows the Log [\ion{O}{ii}] luminosity distribution functions, $p($[\ion{O}{ii}]$| M_r, g-r)$, which we use to assign [\ion{O}{ii}] luminosity to each object. The luminosity is then converted into an [\ion{O}{ii}] flux through 
\begin{equation}
	F = \frac{L}{4\pi D_L}
\end{equation}
where $D_L$ is the luminosity distance \citeeg{Hogg1999}.

\subsection{HETDEX}\label{sec: hetdex}
\begin{figure} 
	\includegraphics[width=\columnwidth]{figures/pointings.pdf} 
	\caption{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings. Each turqoise square represents the position of a single VIRUS IFU, and the dashed octagons approximate the size of a single observation. Inside each IFU HETDEX will achieve near complete coverage through three dithers. See the text for more details.} \label{fig: ifu layout} 
\end{figure}

We designed the results study here to be used with HETDEX, a large blind spectroscopic survey. HETDEX will measure the redshifts of $8 \times 10^5$ LAE galaxies between $1.9 < z < 3.5$ using a collection of 78 wide-field IFU spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}. The goal of these observations will be to provide sub-percent level measurements of the Hubble expansion parameter and the angular diameter distance at $z \sim 2$ via the large scale distribution of galaxies in the redshift range of HETDEX. The result will be a significant constraint on the evolution of dark energy that is competitive with (and independent of) values based on surveys of the Ly$\alpha$ forest.

The entire HETDEX survey will cover 420 \degsq\ with a 1/4.5 filling factor over two fields: a $\sim 300$ \degsq\ northern field, and a $\sim 140$ \degsq\ equatorial region. The $10 \sigma$ detection limit for these spectra will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently for continuum objects, $g = 21.9$ mag. The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$.

The HETDEX IFU pattern is illustrated in Figure~\ref{fig: ifu layout} and consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}. The inter-IFU spacing is also $50''$ spanning a total area of $16'\times 16'$ on the sky. The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing.

@@

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $p(z)$. In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library. See \hbox{\url{http://astlib.sourceforge.net}}}:
\begin{equation}
C_{BI} = M + \frac{\sum_{|u_i| < 1} (z_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
\end{equation}
where $z_i$ are the individual redshifts, $M$ is the median redshift and $u_i$ is given by:
\begin{equation}
	u_i = \frac{(z_i - M)}{C\,\mathrm{MAD}}.
\end{equation}
MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $C$ is the a tuning constant. We choose $C=6$ (the suggested value) which balances computational speed and location accuracy.

@@

We follow the maximum likelihood method of \cite{Walker2006} to estimate the line-of-sight velocity dispersion (LOSVD). We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_{1D}^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_{1D}^2)}\biggr]
\end{equation}
where $\sigma_{1D}$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs (which we have assumed to be normally distributed) respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_{1D} < 1400$ \kms. We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster in Buzzard. When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the square root of second moment of the same distribution, the standard deviation.

@@

\subsubsection{Probability Based}\label{sec:probability method}
For internal consistency between this and the ML based method we use 70\% of the clusters to establish a conditional probability density of $p(M_{200c} | \vec{x})$ which we then use as the cluster mass probability density for the remaining clusters with similar features. In this way we, ``train'' the probability density using the existing simulated data, and apply it to the ``test'' sample (the remaining 30\% of the data not used as the training set).

@@

For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known. To determine the mass probability distribution of a test cluster, $P(M_{200c})$, we combine the conditional probability distribution, $P(M_{200c}|\vec{x})$, created previously with the probability distribution of $\sigma$, the LOSVD, through Equation~\ref{eq: Pm}.
\begin{equation}\label{eq: Pm}
	P(M_{200c}) = \int P(M_{200c}|\vec{x})\ P(\sigma)\ d\sigma
\end{equation}
The expected mass is determined by calculating the first moment of the probability density. This becomes our ``predicted'' cluster mass, $M_{pred}$.
\begin{equation}\label{eq: expected mass}
	M_{pred}= \int M_{200c}\ P(M_{200c})\ dM_{200c}
\end{equation}
The confidence interval associated with this prediction can be estimated two ways. First, by calculating the second moment of the probability density through
\begin{equation}\label{eq: variance}
	\mathrm{Var} = \int (M_{200c} - M_{pred})^2\ P(M_{200c})\ dM_{200c}
\end{equation}
or by drawing many samples from $P(M_{200c})$ and calculating the values at the 16th and 84th percentile. In practice we find that both methods produce similar results for a large number of trials. Therefore, we quote predicted masses as the most probable mass given by Equation~\ref{eq: expected mass} and associated 68\% error estimated through the square root of Equation~\ref{eq: variance}.

@@

\begin{table*}
\centering
\caption{Mean bias (Eqn.~\ref{eqn: bias}) for different bins of predicted cluster mass. This table shows the bias in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins. The different mass recovery strategies are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}
\begin{tabular}{cccccccc} 
		&& \multic{6}{Bins -- Log $M_{pred}$} \\
		\cline{3-8} 
		\multicolumn{2}{c}{Method} & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
		\hline
		&& \multic{6}{Perfect Observations} \\
		\hline 
		\rottext{4}{Prob Based} & Power Law & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
		&$\sigma$ & $0.32\pm{0.005}$ & $0.16\pm{0.003}$ & $0.10\pm{0.002}$ & $0.07\pm{0.004}$ & $0.05\pm{0.012}$ & $-0.18\pm{0.078}$ \\
		&$\sigma, z$ & $0.17\pm{0.005}$ & $0.01\pm{0.003}$ & $-0.06\pm{0.002}$ & $-0.11\pm{0.015}$ & $-0.14\pm{0.012}$ & $-0.38\pm{0.159}$ \\
		&$\sigma, z, N_{gal}$ & $0.04\pm{0.009}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.05\pm{0.014}$ & $-0.22\pm{0.126}$ & $-6.62\pm{3.742}$ \\
		\hline
		\rottext{5}{ML Based} & Power Law & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
		&$\sigma$ & $0.14\pm{0.006}$ & $-0.01\pm{0.003}$ & $-0.07\pm{0.003}$ & $-0.09\pm{0.005}$ & $-0.11\pm{0.014}$ & $-0.17\pm{0.090}$ \\
		&$\sigma, z$ & $0.12\pm{0.005}$ & $-0.01\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.08\pm{0.004}$ & $-0.11\pm{0.012}$ & $-0.24\pm{0.076}$ \\
		&$\sigma, N_{gal}$ & $0.04\pm{0.004}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.006}$ & $-0.08\pm{0.041}$ \\
		&$\sigma, z, N_{gal}$ & $0.04\pm{0.003}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.001}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.005}$ & $-0.08\pm{0.043}$ \\
		\hline

>>>>

\begin{abstract}
\noindent
The distribution of massive clusters of galaxies depends strongly on the total cosmic mass density, the mass variance, and the dark energy equation of state. As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observations of clusters can lead to accurate estimates of their total masses. Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion using probability based and machine learning methods. We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will employ new Visible Integral-Field Replicable Unit Spectrographs (VIRUS), over 420 \degsq\ on the sky with a 1/4.5 fill factor. VIRUS covers the blue/optical portion of the spectrum ($3500-5500~\AAA$), allowing surveys to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$). We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field. For both surveys, we include realistic uncertainties from galaxy magnitude and line-flux limits. We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities. With HETDEX, we can recover cluster masses to $\sim0.1$ dex which can be further improved to $<0.1$ dex with targeted follow-up observations. This level of cluster mass recovery enables constraints on $\sigma_8$ to $<20$\%, and the unique properties of the observations will provide important calibrations for the optical richness-cluster mass relation.
\end{abstract}

@@

The second broad method is the direct calibration of cluster masses. This recipe has two distinct but not always independent tracks. The ``direct'' method uses observations of a relatively small set of clusters and then uses known mass estimators, including X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, microwave observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass. This directly calibrates the observable-mass relation which is then applied to a much larger sample. The complications lie in that the ``true'' masses are, in fact, estimations, and the methods used to recover these cluster masses are subject to their own limitations. X-ray based cluster masses assume hydrostatic equilibrium \citeeg{Mantz2015} which may only be valid for a very small number and range of cluster masses. The Sunyaev-Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up-scattering of cosmic microwave background (CMB) photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a} and can also be effected by the properties of the intracluster medium \citeeg{Pipino2010}. WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters (where the lensing signal is particularly weak), and potentially suffer from line-of-sight effects as WL is sensitive to all mass along the line-of-sight. Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffer from systematics due to cluster formation physics which disrupts the velocity field.

@@

Large-area sky surveys, both on going and planned, are revolutionizing cluster cosmology using a large range of wavelengths. The South Pole Telescope (SPT; \citealt{Carlstrom2011}) and the Atacama Cosmology Telescope (ACT; \citealt{Swetz2011}) are discovering many clusters through the SZE. Optically, the on going Dark Energy Survey (DES; \citealt{DES2005}) and planned Large Synoptic Survey Telescope (LSST; \citealt{LSST2012}) will identify many thousands of clusters to much lower masses than is possible with SZE measurements. However, regardless of the discovery method used, spectroscopic follow-up is needed to further constrain $P(M|z,X)$. This follow-up becomes increasing important to help constrain the scatter in the mass estimates of other methods, and provides an additional, independent check of the observable-mass relationship used. But as the cluster dataset grows to many tens of thousands of clusters individual follow-up becomes increasingly impractical. Therefore, large spectroscopic surveys are needed to more fully understand the observable-mass relation of clusters.

@@

\begin{figure*} 
	\includegraphics[width=0.9\textwidth]{figures/oii_sdss.pdf} 
	\caption{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points. The two colored boxes show regions containing potential catalog galaxies. \textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right. The [\ion{O}{ii}] luminosities are assigned to catalog galaxies from slice sampling the probability histogram and converted to fluxes using the redshift of each galaxy.} \label{fig: oii sdss} 
\end{figure*}

@@

\subsection{Conditional [\ion{O}{ii}] Flux Probability Distribution Functions}\label{sec: oii luminosity}
We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{ii}] emission line strengths to the galaxies in the Buzzard catalog. We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{ii}] line flux signal-to-noise of five. Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies.

@@

Figure~\ref{fig: oii sdss} illustrates this process. The numbered boxes in the left panel show the bins corresponding to two example Buzzard galaxies ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$). The right panel shows the Log [\ion{O}{ii}] luminosity distribution functions, $P($[\ion{O}{ii}]$| M_r, g-r)$, which we use to assign [\ion{O}{ii}] luminosity to each object. The luminosity is then converted into an [\ion{O}{ii}] flux through 
\begin{equation}
	F = \frac{L}{4\pi D_L}
\end{equation}
where $D_L$ is the luminosity distance \citeeg{Hogg1999}.

\subsection{HETDEX}\label{sec: hetdex}
\begin{figure} 
	\includegraphics[width=\columnwidth]{figures/pointings.pdf} 
	\caption{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings. Each turquoise square represents the position of a single VIRUS IFU, and the dashed octagons approximate the size of a single observation. Inside each IFU HETDEX will achieve near complete coverage through three dithers. See the text for more details.} \label{fig: ifu layout} 
\end{figure}

We designed the results of this study to be used in conjunction with HETDEX, a large, blind, spectroscopic survey. HETDEX will measure the redshifts of $8 \times 10^5$ LAE galaxies between $1.9 < z < 3.5$ using a collection of 78 wide-field IFU spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}. The primary science goal of these observations is to provide $<1\%$ accuracy measurements of the Hubble expansion parameter and the angular diameter distance at $z\sim2$. This result will provide significant constraints on the evolution of the dark energy equation of state which is both competitive with, and independent of, constraints derived from observations of the \lya forest.

The entire HETDEX survey will cover 420 \degsq\ with a 1/4.5 filling factor over two fields: a $\sim 300$ \degsq\ northern field, and a $\sim 140$ \degsq\ equatorial region. The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$. The $10 \sigma$ detection threshold for spectral features will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently, $g = 21.9$ mag for continuum objects.

The HETDEX IFU pattern is illustrated in Figure~\ref{fig: ifu layout} by the turquoise squares. Each of the 78 IFUs, are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}. The inter-IFU spacing is also $50''$, spanning a total area of $16'\times 16'$ on the sky. The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing.

@@

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $P(z)$. In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library. See \hbox{\url{http://astlib.sourceforge.net}}}:
\begin{equation}
C_{BI} = M + \frac{\sum_{|u_i| < 1} (z_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
\end{equation}
where $z_i$ are the individual redshifts, $M$ is the median redshift and $u_i$ is given by:
\begin{equation}
	u_i = \frac{(z_i - M)}{C\,\mathrm{MAD}}.
\end{equation}
MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $C$ is the a tuning constant. We choose $C=6$ (the suggested value) which balances computational speed and location accuracy.

@@

We follow the maximum likelihood method of \cite{Walker2006} to estimate the line-of-sight velocity dispersion (LOSVD). We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
P(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_{1D}^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_{1D}^2)}\biggr]
\end{equation}
where $\sigma_{1D}$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs (which we have assumed to be normally distributed) respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_{1D} < 1400$ \kms. We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster in Buzzard. When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the square root of second moment of the same distribution, the standard deviation.

@@

\subsubsection{Probability Based}\label{sec:probability method}
For internal consistency between this and the ML based method we use 70\% of the clusters to establish a conditional probability density of $P(M_{200c} | \vec{x})$ which we then use as the cluster mass probability density for the remaining clusters with similar features. In this way we, ``train'' the probability density using the existing simulated data, and apply it to the ``test'' sample (the remaining 30\% of the data not used as the training set).

@@

For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known. To determine the mass probability distribution of a test cluster, $P(M_{200c})$, we combine the conditional probability distribution, $P(M_{200c}|\vec{x})$, created previously with the probability distribution of $\sigma$, the LOSVD, through Equation~\ref{eq: Pm}.
\begin{equation}\label{eq: Pm}
	P(M_{200c}) = \int P(M_{200c}|\vec{x})\ P(\sigma)\ d\sigma\ P(z)\ dz
\end{equation}
The expected mass is determined by calculating the first moment of the probability density. This becomes our ``predicted'' cluster mass, $M_{pred}$.
\begin{equation}\label{eq: expected mass}
	M_{pred}= \int M_{200c}\ P(M_{200c})\ dM_{200c}
\end{equation}
The confidence interval associated with this prediction can be estimated two ways. First, by calculating the second moment of the probability density through
\begin{equation}\label{eq: variance}
	\mathrm{Var} = \int (M_{200c} - M_{pred})^2\ P(M_{200c})\ dM_{200c}
\end{equation}
or by drawing many samples from $P(M_{200c})$ and calculating the values at the 16th and 84th percentile. In practice we find that both methods produce similar results for a large number of trials. Therefore, we quote predicted masses as the most probable mass given by Equation~\ref{eq: expected mass} and associated 68\% error estimated through the square root of Equation~\ref{eq: variance}.

@@

\begin{table*}
\centering
\caption{Mean bias (Eqn.~\ref{eqn: bias}) for different bins of predicted cluster mass. This table shows the bias in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins. The different mass recovery strategies are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}
\begin{tabular}{cccccccc} 
		&& \multic{6}{Bins -- Log $M_{pred}$} \\
		\cline{3-8} 
		\multicolumn{2}{c}{Method} & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
		\hline
		&& \multic{6}{Perfect Observations} \\
		\hline
		\multicolumn{2}{c}{Power Law} & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
		\hline 
		\rottext{3}{Prob} &$\sigma$ & $0.32\pm{0.005}$ & $0.16\pm{0.003}$ & $0.10\pm{0.002}$ & $0.07\pm{0.004}$ & $0.05\pm{0.012}$ & $-0.18\pm{0.078}$ \\
		&$\sigma, z$ & $0.17\pm{0.005}$ & $0.01\pm{0.003}$ & $-0.06\pm{0.002}$ & $-0.11\pm{0.015}$ & $-0.14\pm{0.012}$ & $-0.38\pm{0.159}$ \\
		&$\sigma, z, N_{gal}$ & $0.04\pm{0.009}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.05\pm{0.014}$ & $-0.22\pm{0.126}$ & \nd \\
		\hline
		\rottext{4}{ML} &$\sigma$ & $0.14\pm{0.006}$ & $-0.01\pm{0.003}$ & $-0.07\pm{0.003}$ & $-0.09\pm{0.005}$ & $-0.11\pm{0.014}$ & $-0.17\pm{0.090}$ \\
		&$\sigma, z$ & $0.12\pm{0.005}$ & $-0.01\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.08\pm{0.004}$ & $-0.11\pm{0.012}$ & $-0.24\pm{0.076}$ \\
		&$\sigma, N_{gal}$ & $0.04\pm{0.004}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.006}$ & $-0.08\pm{0.041}$ \\
		&$\sigma, z, N_{gal}$ & $0.04\pm{0.003}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.001}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.005}$ & $-0.08\pm{0.043}$ \\
		\hline

		&& \multic{6}{Targeted Observations} \\
		\hline
		\multicolumn{2}{c}{Power Law} & $0.20\pm{0.008}$ & $0.13\pm{0.005}$ & $0.10\pm{0.005}$ & $0.09\pm{0.007}$ & $0.02\pm{0.014}$ & $-0.08\pm{0.043}$ \\
		\hline
		\rottext{3}{Prob} &$\sigma$ & $0.40\pm{0.005}$ & $0.17\pm{0.003}$ & $0.02\pm{0.004}$ & $-0.08\pm{0.006}$ & $-0.19\pm{0.015}$ & $-0.35\pm{0.122}$ \\
		&$\sigma, z$ & $0.25\pm{0.005}$ & $0.08\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.21\pm{0.015}$ & $-0.35\pm{0.016}$ & $-0.59\pm{0.145}$ \\
		&$\sigma, z, N_{gal}$ & $0.13\pm{0.004}$ & $0.01\pm{0.003}$ & $-0.05\pm{0.003}$ & $-0.12\pm{0.018}$ & $-0.44\pm{0.177}$ & \nd \\
		\hline
		\rottext{4}{ML} &$\sigma$ & $0.26\pm{0.006}$ & $0.02\pm{0.004}$ & $-0.13\pm{0.005}$ & $-0.24\pm{0.008}$ & $-0.35\pm{0.022}$ & $-0.39\pm{0.054}$ \\
		&$\sigma, z$ & $0.18\pm{0.005}$ & $0.03\pm{0.003}$ & $-0.10\pm{0.004}$ & $-0.21\pm{0.006}$ & $-0.31\pm{0.021}$ & $-0.33\pm{0.063}$ \\
		&$\sigma, N_{gal}$ & $0.22\pm{0.005}$ & $0.00\pm{0.004}$ & $-0.13\pm{0.004}$ & $-0.16\pm{0.007}$ & $-0.13\pm{0.014}$ & $-0.19\pm{0.059}$ \\
		&$\sigma, z, N_{gal}$ & $0.09\pm{0.004}$ & $-0.01\pm{0.002}$ & $-0.05\pm{0.002}$ & $-0.08\pm{0.004}$ & $-0.08\pm{0.010}$ & $-0.19\pm{0.060}$ \\
		\hline
